Rapid cycleway prioritisation tool

### 2020-06-04 code/index.Rmd
Update intro sentences

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
In the context of COVID-19, big decisions need to be made **rapidly**.

The rapid cycleway prioritisation tool aims to help produce evidence-based answers the question: **where to reallocate road space on arterial routes away from motor traffic and towards active transport?**
The focus of the tool is road space reallocation on strategic corridors, a key way in which transport systems can be transformed to overcome capacity constraints on public transport modes and prevent gridlock as the lockdown eases.

>>>>

The [rapid cycleway prioritisation tool](https://www.cyipt.bike/rapid/) helps identify promising locations for road space reallocation in England to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
In the context of COVID-19, big decisions need to be made **rapidly**.

The rapid cycleway prioritisation tool aims to help produce evidence-based answers the question: **where to reallocate road space on strategic corridors away from motor traffic to enable uptake of cycling?**
The focus of the tool is road space reallocation on strategic corridors, a key way in which transport systems can be transformed to overcome capacity constraints on public transport modes and prevent gridlock as the lockdown eases.
